---
title: "IFS586"
author: "Szymon Górka Justyna Zagórwoicz"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

IFS586 package creates fractals by method IFS. The package contains the following functionalities: 
- creates object S3 form contraction functions
- plot fractals from object IFS_S3

## Examples

Pakcage contaons varius examples of fractals constructed by method IFS. 
 
First define contractions functions and probability vector
```{r, include=FALSE}
library(IFS586)
f1<-function(x,y){
  x<-0.5*x - 0.5
  y<-0.5*y + 0.5
  return(c(x,y))
}

f2<-function(x,y){
  x<-0.5*x - 0.5
  y<-0.5*y - 0.5
  return(c(x,y))
}

f3<-function(x,y){
  x<-0.5*x + 0.5
  y<-0.5*y - 0.5
  return(c(x,y))
}

p<-c(0.3333, 0.3333, 0.3334)
sierpisnki <- createIFS(f1, f2, f3, prob_vec=p)
```
The you can use overloaded function plot:
```{r}
plot(sierpisnki, n=15)

```



## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
